Efficient and Scalable Bipartite Matching with Fast Beta Linkage (fabl)

### 2022-09-20 ba_resubmit/response_to_reviewers.tex

	\reply{%
		\textcolor{red}{BEKA/JERRY: I think this reviewer wants us to explicitly mention Sadinle in the abstract. I think I had that originally, but we removed it. Please advise on the best way to address this comment.}
	}

\newpage

\section{Additional Points Addressed}

We highlight some additional points addressed in our revision. \todo
\textcolor{blue}{Brian: These are just some suggestions that I have, so we can chat through these in case you don't agree! I have these marked up on a printed copy of the paper itself to help you more easily make the changes. Please note I have not made these changes, but I'm marking them on a marked up paper so you can go back through and make changes. It's likely that there may be more errors, so please go over things very carefully for all errors as the content is all there, we just have to weed out these tedious details.}

\begin{enumerate}
\item We have added introductory sentences to each section/subsection to provide more guidance to the reader. 
\item The word databases is used throughout instead of files or lists. 
\item We have checked for the proper use of commas throughout the paper. 
\item We have re-written our proposed work on page 2 to make it more clear our contributions to the literature as it was missing our improvements over existing work in terms of speed with minimal loss in accuracy as well as providing two case studies. One case study is from the original paper of our extension, while another case study illustrates our ability to scale to larger databases. We provide a more comprehensive discussion regarding our work. 
\item We have broken up sentences that are too long.
\item We have removed repetitive words, such as intuitive, additionally.  \textcolor{blue}{Brian: you can use something like antidote to check for these or go through yourself. Be careful with the word intuitive. While it might be obvious to you, it may not be obvious to the Editor and this word can be quite jarring). As an example, in my job talk, Mike West did not find the linkage structure to be intuitive and found it to be quite weird and confusing!}
\item We have checked that we define terms before they are introduced. 
\item We have defined the parameters $m$ and $u$ on page 4. 
\item One page 5, section 2.2, we have made it more clear why our extension is warranted and needed in the literature. 
\item We have removed confusing language, such as "compactful representation of" on page 5. 
\item We have checked that fast beta linkage is represented by fabl throughout. 
\item \textcolor{blue}{See page 10 for a long list of comments.}
\item We do not start sentences with a Greek letter or a parameter.
\item We have fixed the sentence ``sampling a value from...." that has a missing verb (see page 11).
\item We have fixed a typo in equation 6, which is a missing (). 
\item We have corrected many typos in section 5.1 page 12 (first paragraph). These include a comma that should not be present, a period instead of a comma, and a Greek letter that starts a sentence.
\item Break up the first long sentence in Lemma 1 as it's hard to read. 
\end{enumerate}
\end{document}

### 2022-09-20 ba_resubmit/kundinger_resubmit.tex
update nltcs.

	The National Long Term Care Study (NLTCS) is a longitudinal study tracking the health outcomes of Medicare recipients. The initial survey began in 1982, with follow-up surveys taken approximately every five years. For this study, we seek to link records over the $n_1 = 20485$ records from 1982 to the $n_2 = 17466$ records from 1989. \textcolor{red}{In each iteration of the study, some participants are added to the lists, and others are lost due to loss of contact or death.} The NLTCS data have longitudinal links, so that in reality one does not need to conduct record linkage.  However, following the strategy in \cite{guha:reiter:BA} we break the longitudinal links and treat the data from 1982 and 1989 as stand-alone files.

>>>>

	The National Long Term Care Study (NLTCS) is a longitudinal study tracking the health outcomes of Medicare recipients. The initial survey began in 1982, with follow-up surveys taken approximately every five years. For this study, we seek to link records over the $n_1 = 20485$ records from 1982 to the $n_2 = 17466$ records from 1989. \textcolor{blue}{Within each database there are no duplications, however, there can be duplications across the databases. In addition, patients can either drop out of the study, pass away, or enter as new patients. Hence, the assumptions of our model hold for this study.}
%	\textcolor{red}{In each iteration of the study, some participants are added to the lists, and others are lost due to loss of contact or death.} 
	The NLTCS data have longitudinal links, so that in reality one does not need to conduct record linkage.  However, following the strategy in \cite{guha:reiter:BA}, we break the longitudinal links and treat the data from 1982 and 1989 as stand-alone databases.
